Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-07 tex/paper1/paper1.tex
edits to the paper

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - <I(t)>)/<I(t)>$.
This normalizes the emission.  Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects.  This
results in a time-series from which its Fourier power spectrum was
analyzed.

Figures \ref{fig:compare171193} show example power spectra, plotted using
a log-log scale, from a single location inside each of the regions
shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies and flattens out at higher
frequencies.

@@

Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for certain frequencies in the
spectrum.  The distributions all approximately follow a normal
distribution.  This indicates that the power in each each at each
frequency is approximately log-normally distributed.  This observation
guides the choice of how to average the power spectrum over each of
the selected physical regions.  Since the Fourier power is
log-normally distributed, the arithmetic mean of the Fourier power is
biased by the very largest powers.  Hence the mean of the logarithm of
the Fourier power is considered, which is equivalent to the geometric
mean of the Fourier power.

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see
  also Figure \ref{fig:dist171} for the corresponding AIA
  171\AA\ plots.)}
\label{fig:dist193}
\end{figure}

These geometric mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.

@@

The results for the quiet Sun, loop footpoints and sunspot regions
suggest a power-law power spectrum.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  Previous studies (???) have shown that the moss is a source
of Fourier power.  This suggests that a second model $M_{2}$ for these
regions should be considered.  The second model $M_{2}$ has two
contributions to the overall \Fps; a background power-law of the form
of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

As has been shown above, the assumption of a Gaussian-distributed
noise when red noise power-spectrum is actually present, coupled with
too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many detection algorithms do make
this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
\cite{2010SoPh..264..403I}.  Such approaches have yet to be tested
assuming a red-noise background power spectrum, and so their efficacy
is unknown.  \cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S}
are wavelet-based approaches, and Figure \ref{fig:comparison} does
suggest that a red-noise background spectrum will make a significant
difference.

@@

We are grateful to the developers of SSWIDL \cite{}, SunPy \cite{},
PyMC \cite{} and matplotlib \cite{} for providing data preparation,
manipulation, analysis and display packages.  This work was supported
by the NASA....

>>>>

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
power spectrum.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a power law at lower frequencies, and flattens out at higher
frequencies.

@@

@@

\begin{figure}
\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
\caption{Distribution of Fourier power at some sample frequencies (see
  also Figure \ref{fig:dist171} for the corresponding AIA
  171\AA\ plots.)}
\label{fig:dist193}
\end{figure}
Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
of the logarithm of the Fourier power for a small number of
frequencies, for all the pixels in each region.  The distributions all
follow a normal distribution approximately.  This indicates that the
power in each each at each frequency is approximately log-normally
distributed.  This observation guides the choice of how to average the
power spectrum over each of the selected region.  Since the Fourier
power is log-normally distributed, the arithmetic mean of the Fourier
power is biased by the very largest powers.  Since the logarithm of
the Fourier power is approximately Gaussian-distributed, the mean
value is a better representation of the range of values in the data.
Hence the mean of the logarithm of the Fourier power is used to
describe the mean Fourier power spectrum of each region (note that
this is also equivalent to the geometric mean of the Fourier power.)

@@

The (geometric) mean Fourier power spectra are shown in Figures
\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
regions considered.  It is clear that, in general, the Fourier power
spectra exhibit power-law like characteristics.  The results for the
quiet Sun, loop footpoints and sunspot regions suggest a power-law
power spectrum.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the power law index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that the bright upper
transition region emission above active region plage (also known as
moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.

This suggests that a second model
$M_{2}$ for these regions should be considered.  The second model
$M_{2}$ has two contributions to the overall \Fps; a background
power-law of the form of $P_{1}$, and a contribution that is more
localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

As has been shown above, the assumption of a Gaussian-distributed
noise when red noise power-spectrum is actually present, coupled with
too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many detection algorithms do make
this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
approaches have yet to be tested assuming a red-noise background power
spectrum, and so their efficacy is unknown.
\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
wavelet-based approaches, and Figure \ref{fig:comparison} does suggest
that a red-noise background spectrum will make a significant
difference.

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013}, PyMC
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific Python
stack for providing data preparation, manipulation, analysis and
display packages.  This work was supported by the NASA award number????
